---
title: "sampling_strategy"
output: html_document
date: '2022-06-01'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Loading the data
```{r, message = FALSE}
library(readr)
library(dplyr)
library(data.table)
```

We want to take a sample total of approx 30m
```{r}
# lets say there's 175m tweets here, and we want approx 30m, we want 17%
set.seed(1)
options(scipen = 100)
sampling <- function(tsv){
  data <- read_tsv(file = tsv, col_names = TRUE)
  
  # only English language tweets
  data <- data %>% filter(lang == "en")
  
  # changing the format of the date_time 
  data$date_time <- as.IDate(data$date_time)
  
  print(unique(data$date_time))
  # vector of all dates
  dates <- unique(data$date_time)
  
  # empty vector to store tweet ids
  tweet_ids <- c()
  
  # goes through each date and takes a random sample of 8% of the tweets for that day
  for (i in dates){
    
    # tweets from date i
    sampled <- data %>% 
      filter(date_time == i)
    
    # finds the number of tweets to select to have 8%
    n <- nrow(sampled)
    s <- floor(0.17*n)
    
    # randomly samples from the indexes of the sample data
    sample_ix <- sample(1:nrow(sampled), size = s)
    ix <- sampled[sample_ix,]$tweet_id
    
    # adds the tweet ids of the randomly sampled to the vector
    tweet_ids <- c(tweet_ids, ix)
  }

  # finally, sampling from the data 
  the_sample <- data %>%
    filter(tweet_id %in% tweet_ids)
  
  return(the_sample)
}


TBCOVaustralia_01 <- sampling("../australia_tbcov/australia_1.tsv")
TBCOVaustralia_02 <- sampling("../australia_tbcov/australia_2.tsv")

TBCOVaustralia <- rbind(TBCOVaustralia_01,TBCOVaustralia_02)
write.csv(TBCOVaustralia, "../sampled_data/TBCOVaustralia.csv")

TBCOVcanada_01 <- sampling("../canada_tbcov/canada_1.tsv")
TBCOVcanada_02 <- sampling("../canada_tbcov/canada_2.tsv")
TBCOVcanada_03 <- sampling("../canada_tbcov/canada_3.tsv")
TBCOVcanada_04 <- sampling("../canada_tbcov/canada_4.tsv")
TBCOVcanada_05 <- sampling("../canada_tbcov/canada_5.tsv")

TBCOVcanada <- rbind(TBCOVcanada_01,TBCOVcanada_02,TBCOVcanada_03,TBCOVcanada_04,TBCOVcanada_05)
write.csv(TBCOVcanada, "../sampled_data/TBCOVcanada.csv")

TBCOVireland <- sampling("../ireland_tbcov/ireland_tbcov.tsv")

write.csv(TBCOVireland, "../sampled_data/TBCOVireland.csv")
TBCOVnew_zealand <- sampling("../new_zealand_tbcov/new_zealand_tbcov.tsv")
write.csv(TBCOVnew_zealand, "../sampled_data/TBCOVnew_zealand.csv")

TBCOVuk_01 <- sampling("../united_kingdom_tbcov/united_kingdom_01.tsv")
TBCOVuk_02 <- sampling("../united_kingdom_tbcov/united_kingdom_02.tsv")
TBCOVuk_03 <- sampling("../united_kingdom_tbcov/united_kingdom_03.tsv")
TBCOVuk_04 <- sampling("../united_kingdom_tbcov/united_kingdom_04.tsv")
TBCOVuk_05 <- sampling("../united_kingdom_tbcov/united_kingdom_05.tsv")

TBCOVuk_01 <- rbind(TBCOVuk_01,TBCOVuk_02,TBCOVuk_03,TBCOVuk_04,TBCOVuk_05)
write.csv(TBCOVuk_01, "../sampled_data/TBCOVuk_01.csv")

TBCOVuk_06 <- sampling("../united_kingdom_tbcov/united_kingdom_06.tsv")
TBCOVuk_07 <- sampling("../united_kingdom_tbcov/united_kingdom_07.tsv")
TBCOVuk_08 <- sampling("../united_kingdom_tbcov/united_kingdom_08.tsv")
TBCOVuk_09 <- sampling("../united_kingdom_tbcov/united_kingdom_09.tsv")
TBCOVuk_10 <- sampling("../united_kingdom_tbcov/united_kingdom_10.tsv")
TBCOVuk_11 <- sampling("../united_kingdom_tbcov/united_kingdom_11.tsv")

TBCOVuk_02 <- rbind(TBCOVuk_06,TBCOVuk_07,TBCOVuk_08,TBCOVuk_09,TBCOVuk_10, TBCOVuk_11)
write.csv(TBCOVuk_02, "../sampled_data/TBCOVuk_02.csv")

```
### Redoing the sample
After running an initial hydration of the ireland and nz tweets, counting the number retrieved and the number of duplicated texts, I decided to resample, and randomly reduce the number of tweets to 0.35 of the original size.
I intend to have approximately 1m unique tweets in my active learning model.
```{r}
set.seed(1)
ireland<- read_csv("C:/Users/kcrow/Documents/Capstone/sampled_data/TBCOVireland.csv")
new_zealand <- read_csv("C:/Users/kcrow/Documents/Capstone/sampled_data/TBCOVnew_zealand.csv")
australia<- read_csv("C:/Users/kcrow/Documents/Capstone/sampled_data/TBCOVaustralia.csv")
canada <- read_csv("C:/Users/kcrow/Documents/Capstone/sampled_data/TBCOVcanada.csv")
uk_01 <- read_csv("C:/Users/kcrow/Documents/Capstone/sampled_data/TBCOVuk_01.csv")
uk_02 <- read_csv("C:/Users/kcrow/Documents/Capstone/sampled_data/TBCOVuk_02.csv")

#lets reduce it to 1/3 for the remaining ones, and also randomly sample 1/3 of the ireland and nz ones
random_sample <- function(data, proportion){
  # finds the number of tweets to select to have 8%
  n <- nrow(data)
  s <- floor(proportion*n)
    
  # randomly samples from the indexes of the sample data
  sample_ix <- sample(1:nrow(data), size = s)
  
  data <- data[sample_ix,]
  
  return(data)
}

options(scipen = 100)
australia_sample <- random_sample(australia, 0.35)
tweet_ids <- australia_sample$tweet_id
write.table(tweet_ids, "../tweet_ids/tweets_australia.txt", sep = "/n",
            row.names = FALSE, col.names = FALSE)
write.csv(australia_sample, "C:/Users/kcrow/Documents/Capstone/sampled_data/TBCOVaustralia.csv")

options(scipen = 100)
canada_sample <- random_sample(canada, 0.35)
tweet_ids <- canada_sample$tweet_id
write.table(tweet_ids, "../tweet_ids/tweets_canada.txt", sep = "/n",
            row.names = FALSE, col.names = FALSE)
write.csv(canada_sample, "C:/Users/kcrow/Documents/Capstone/sampled_data/TBCOVcanada.csv")

# I am not producing a txt file for this as I have already retrieved all tweets for ireland and nz
options(scipen = 100)
ireland_sample <- random_sample(ireland, 0.35)
write.csv(ireland_sample, "C:/Users/kcrow/Documents/Capstone/sampled_data/TBCOVireland.csv")

options(scipen = 100)
new_zealand_sample <- random_sample(new_zealand, 0.35)
write.csv(new_zealand_sample, "C:/Users/kcrow/Documents/Capstone/sampled_data/TBCOVnew_zealand.csv")

options(scipen = 100)
uk_01_sample <- random_sample(uk_01, 0.35)
tweet_ids <- uk_01_sample$tweet_id
write.table(tweet_ids, "../tweet_ids/tweets_uk_01.txt", sep = "/n",
            row.names = FALSE, col.names = FALSE)
write.csv(uk_01_sample, "C:/Users/kcrow/Documents/Capstone/sampled_data/TBCOVuk_01.csv")

options(scipen = 100)
uk_02_sample <- random_sample(uk_02, 0.35)
tweet_ids <- uk_02_sample$tweet_id
write.table(tweet_ids, "../tweet_ids/tweets_uk_02.txt", sep = "/n",
            row.names = FALSE, col.names = FALSE)
write.csv(uk_02_sample, "C:/Users/kcrow/Documents/Capstone/sampled_data/TBCOVuk_02.csv")

```

